---
title: "1995-03 Dashboard"
subtitle: "Monthly Dashboard for Beer sold at Dominick's: March 1995"
draft: true
format:
  html:
    toc: true
    toc-expand: 2

categories:
  - Dominicks
  - Beer
  - GEKS
---

# Overview

```{r}
#| echo: false
#| warning: false

period <- "1995-03"
category_name <- "ber"

source("R/diagnostics.R")


bar_df <- overview_table(period, category_name)

datatable(bar_df, options = list(
  dom = 't' # i.e. Table only
))
```

# Diagnostics

## Analytical (output) diagnostics

Contributions (multiplicative decomposition) compared to the product's average recent share (MoM)

```{r}
#| echo: false
#| warning: false

source("R/price_indices.R")

products_and_contribution <- GEKS_contributions(category_name, period)

p <- ggplot(products_and_contribution, aes(x = log_contribution, y = Avg_Share, text = paste(
    "NITEM:", product,
    "<br>MoM relative:", Price_Ratio,
    "<br>Log contribution:",log_contribution
  ))) +
    geom_point(alpha = 0.5, color = "#3498db") +
    # geom_hline(yintercept = 1, linetype = "dashed", color = "#392f2f") +
    theme_minimal() +
    labs(x = "log contribution", y = "Average Share")
  
  ggplotly(p, tooltip = "text")

```

Similarly, contributions (multiplicative decomposition) compared to the product's relative (MoM)

```{r}
p <- ggplot(products_and_contribution, aes(x = log_contribution, y = Price_Ratio, text = paste(
    "NITEM:", product,
    "<br>Average share:", Avg_Share,
    "<br>Log contribution:",log_contribution
  ))) +
    geom_point(alpha = 0.5, color = "#3498db") +
    # geom_hline(yintercept = 1, linetype = "dashed", color = "#392f2f") +
    theme_minimal() +
    labs(x = "log contribution", y = "MoM relative")
  
  ggplotly(p, tooltip = "text")
```


## Input diagnostics

### Churn over time

Churn over time - plotting products (`NITEM`) entering the sample, products staying (compared to the previous period) and products leaving the sample (i.e. not seen this month).

```{r}
#| echo: false
#| warning: false

ird <- read_parquet(glue("data/clean/ird_{category_name}_timesamp_NULL_groupby_NITEM-REF_PERIOD.parquet"))

data_up_to_period <- ird %>%
      filter(REF_PERIOD <= period)

plot_product_churn(data_up_to_period)
```

### Item-level price relatives

```{r}
#| echo: false
#| warning: false

unit_price_changes <- item_price_ratio_table(data_up_to_period, period)
```

::: panel-tabset
## Plot of price change by share

```{r}
#| echo: false
#| warning: false

plot_item_price_relatives(unit_price_changes)
```

## Raw data

```{r}
#| echo: false
#| warning: false

datatable(unit_price_changes)
```
:::

## Monitoring / data validation

### Weeks in scope

The following weeks' data was used a input for the last month.

```{r}
#| echo: false
#| warning: false

results <- monitoring_stats(period, category_name)

results$period_data <- results$period_data[, c(
  "WEEK", 
  "week_start", 
  "week_end", 
  "distinct_upcs",
  "distinct_nitems",
  "total_sales",
  "number_of_rows",
  "distinct_stores",
  "distinct_com_codes",
  "distinct_zones",
  "ref_period")]

datatable(
      results$period_data,
      extensions = 'Buttons', # For the colvis button
      options = list(
        # 'B' adds buttons, 't' is the table
        dom = 'Bt', 
        buttons = c('colvis'),
        columnDefs = list(
          list(
            visible = FALSE,      # Hide columns by default
            targets = c(4, 8, 9, 10, 11)     # Hide a few to simplify UI
          )
        ),
        # Force table to occupy full container width
        autoWidth = TRUE,
        width = '100%'
      )
    )
```

### Week by week breakdown

```{r}
#| echo: false
#| warning: false

library(plotly)
library(htmltools)

widgets <- plot_weekly_stats(results$period_data, results$weekly_stats)
widgets
```